**The status of the microbial census: an update**

### 2015-12-05 results/tables/build_environmental_categories_table.Rmd
Add table for environmental categories

---
output:
  pdf_document:
    includes:
      in_header: table_header.tex
tables: true
geometry: margin=1.0in
---

**Supplemental Table 1. Description of environmental categories and the criteria used to assign sequences to each category.**

@@

categories <- c(AE="Aerosol", AQB="Brackish", AQBS="Brackish sediment", AQF="Freshwater", AQFS="Freshwater sediment", AQM="Marine", AQMS="Marine sediment", AQH="Hydrothermal vent", AQI="Ice", AQO="Aquatic other", BD="Digesters", BF="Food-associated", BI="Industrial/mining", BP="Pollution associated", BO="Built other", PR="Plant root", PS="Plant surface", PO="Plant other", SA="Agricultural soil", SD="Desert soil", SP="Permafrost", SO="Other soils", ZV="Vertebrate", ZA="Arthropod", ZN="Other invertebrate", ZO="Other zoological", OT="Other")

@@

coarse <- c("Aerosol", "Aquatic", "", "", "", "", "", "", "", "", "Built", "", "", "", "", "Plant associated", "", "", "Soil", "", "", "", "Zoological", "", "", "", "Other")

@@

colnames(text) <- paste0("\\textbf{", c("Coarse", "Category", "Description"), "}")
composite <- xtable(text)
align(composite) <- "lllp{11cm}"
print(composite, include.rownames=FALSE, include.colnames=TRUE, hline.after = seq(-1, nrow(composite)), comment=FALSE, size="footnotesize")

```

>>>>

---
output:
  pdf_document:
    includes:
      in_header: table_header.tex
    template: notitle.tex
tables: true
geometry: margin=1in
---

\captionsetup{labelformat=empty}

@@

categories <- c(AE="", AQB="Brackish", AQBS="Brackish sediment", AQF="Freshwater", AQFS="Freshwater sediment", AQM="Marine", AQMS="Marine sediment", AQH="Hydrothermal vent", AQI="Ice", AQO="Other", BD="Digesters", BF="Food-associated", BI="Industrial/mining", BP="Pollution associated", BO="Other", PR="Plant root", PS="Plant surface", PO="Other", SA="Agricultural soil", SD="Desert soil", SP="Permafrost", SO="Other", ZV="Vertebrate", ZA="Arthropod", ZN="Other invertebrate", ZO="Other", OT="")

@@

coarse <- c("\\midrule\\multirow{2}{*}{Aerosol}",
			"\\midrule\\multirow{16}{*}{Aquatic}", "", "", "", "", "", "", "", "",
			"\\midrule\\multirow{11}{*}{Built}", "", "", "", "",
			"\\midrule\\multirow{6}{*}{Plant associated}", "", "",
			"\\midrule\\multirow{6}{*}{Soil}", "", "", "",
			"\\midrule\\multirow{6}{*}{Zoological}", "", "", "",
			"\\midrule\\multirow{2}{*}{Other}")

@@

colnames(text) <- paste0("\\textbf{", c("Coarse", "Fine", "Description"), "}")

addtorow <- list(pos=as.list(1:nrow(text)),
				command=c('',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'\\cmidrule(r){2-3}',
						'',
						'')

						)

caption <- "\\textbf{Supplemental Table 1. Description of environmental categories and the criteria used to assign sequences to each category.}"

composite <- xtable(text, caption=caption, label="")
align(composite) <- "lllp{10cm}"
print(composite, include.rownames=FALSE, include.colnames=TRUE, hline.after = c(-1, nrow(composite)), comment=FALSE, add.to.row=addtorow, caption.placement = "top", size="footnotesize")
```
